### 2011-08-18 doc/theses/vitasek/chapter-4-experiments.tex
Thesis: in progress.

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & TODO \\
  Input data        & all official and sized test data sets \\
  Iterations        & 20 \\
  Pool size         & not applicable \\
  $\alpha$, $\beta$ & not applicable \\
  \hline
\end{tabular}
\bigskip
\end{center}

The experimental set will contain $20 * (11 + 11) = 440$ configurations: 20 iterations for 11 test data sets plus 11 sized test data sets. There will be no CHs or IHs. We will be gathering the timing data for IG extraction and model generation in GnuPlot format.

@@

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Dual Core \\
  Input data        & \texttt{100-500} \\
  Iterations        & 20 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}

Our experimental set will contain 500 experimental configurations for each of these two GLPK version. Every configuration will use \heu{Glpk} CH set to a time limit from 1 to 49 seconds with increments of 2, meaning 25 settings * 20 iterations = 500 configurations in total (see Listing \ref{listing-experiment-glpk-native-vs-cygwin-1}). There will be no improvement heuristic. The only data we gather in the GnuPlot file are the final qualities (weights).

@@

>>>>

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & TODO \\
  Input data        & all official and sized test data sets \\
  Iterations        & 50 \\
  Pool size         & not applicable \\
  $\alpha$, $\beta$ & not applicable \\
  \hline
\end{tabular}
\bigskip
\end{center}

The experimental set will contain $50 * (11 + 11) = 1100$ configurations: 20 iterations for 11 test data sets plus 11 sized test data sets. There will be no CHs or IHs. We will be gathering the timing data for IG extraction and model generation in GnuPlot format.

TODO just table (mean, variance), no chart + interpretation

@@

\begin{center}
\bigskip
\begin{tabular}{| l | l |}
  \hline
  \hline
  Machine           & Dual Core \\
  Input data        & \dataset{100-500} \\
  Iterations        & 50 \\
  Pool size         & 1 \\
  $\alpha$, $\beta$ & $1$, $1$ \\
  \hline
\end{tabular}
\bigskip
\end{center}

Our experimental set will contain 500 experimental configurations for each of these two GLPK version. Every configuration will use \heu{Glpk} CH set to a time limit from 1 to 46 seconds with increments of 5, meaning 10 settings * 50 iterations = 500 configurations in total (see Listing \ref{listing-experiment-glpk-native-vs-cygwin-1}). There will be no improvement heuristic. The only data we gather in the GnuPlot file are the final qualities (weights).

@@

TODO try this on XMA-p
